\section{Group Members Contribution}

% For each group member, describe in detail the contribution to the project.

\begin{description}
	\item[Parisa Saeedidana] \hfill
	    \begin{itemize}
		\item Defined and updated the project objectives.
		\item Created the initial ER diagram and wrote the description of the ER schema.
		\item Developed DAO classes for: Publisher, Reviews, Author, Book, including authentication functionality.
		\item Implemented REST scripts for: Shopping cart operations and User managemnet.
		\item Developed servlets for: Book operations, shoppig cart, search and home page.
		\item Designed and implemented JSP pages for: Author, Book, Search results and Wishlist.
		\item Added additional test data to the database.
		\item Created the DAO class diagram and the User Registration sequence diagram for the report.
		\item Contributed to the overall progress and coordination of the project.
		\end{itemize}

	\item[Amirreza Jolani mameghani] \hfill    
	\begin{itemize}
		\item Edited ER diagram and helped to write the ER schema description.
		\item Wrote the Docker for the project, and created a database folder and write sql code of the project.
		\item implemented the resource folder of the project.
		\item developed all the utilites of project ErrorCode and JWT Utils.
		\item developed the whole services folder(validation) for the project.
		\item Developed the servlets for admin, image, order.
		\item developed wishlist, User DAO classes for the project and try to modify the code of other DAO classes.
		\item Wrote mostly the queries for all DAO classes.
		\item Implemented REST for classes and modified other teammates' files to fix.
		\item Contributed to the overall progress and coordination of the project.
	\end{itemize}

	\item[Ayoub Ben Yamoune] \hfill	    
	\begin{itemize}
		\item Wrote the presentation section of the report and created all associated mockups.
		\item Developed the DAO classes for Order and User.
		\item Developed the servlets for User and Book.
		\item Designed and implemented the JSP pages for User and Registration.
		\item Contributed to the overall progress and coordination of the project.
	\end{itemize}
	
	\item[Md Abu Raihan Mia:] \hfill
	\begin{itemize} 
	\item Wrote REST API Summary, REST Error Codes and REST API Details for the report.
	\item Designed and implemented the JSP page for the All Publishers.
	\item Fixed REST error codes and implemented the \texttt{ErrorCode} page.
	\item Created and designed the AuthorServlet sequence diagram for the report.
	\item Contributed to the overall progress and coordination of the project.
	\end{itemize}

	\item[Adam Truty] \hfill
	\begin{itemize}
		\item Developed DAO classes for: Discount, Category, and Cart.
		\item Implemented the servlets for: Cart and Author.
		\item Designed and implemented the JSP page for the Cart.
		\item Created and wrote the report sections for the sequence diagrams (CartServlet and BookServlet).
		\item Created and described the Class Diagram of the application for the report.
		\item Assisted in debugging and resolving issues during the development process.
		\item Contributed to the overall progress and coordination of the project.
	\end{itemize}

\end{description}
