\section{Objectives}
%Brief description of the overall objectives of your system.
%What your system will be used for? Why is it important? What problems does it solve?

The bookstore web application aims to provide an intuitive, feature-rich, and user-friendly platform for browsing, purchasing, and managing books online. The primary objective of this project is to enhance the online book-shopping experience by offering users a well-organized and efficient system where they can explore books, add them to their shopping cart or wishlist, leave reviews, apply discounts, and securely complete their purchases.
This application is designed for book enthusiasts who want a convenient way to discover and buy books without visiting a physical store. Users can create an account, browse books by category, author, or publisher, and use additional features like wishlists to save books for future purchases. The wishlist functionality allows users to keep track of books they are interested in without immediately adding them to their shopping cart, enhancing flexibility in decision-making.
A key feature of the system is the shopping cart, where users can add multiple books before proceeding to checkout. The ordering system ensures a structured purchasing process, allowing users to place orders and complete payments securely. Payment transactions include details such as the amount, method, and date, ensuring transparency and security. The discount feature provides users with promotional offers through discount codes, enhancing the affordability of books and improving customer satisfaction.
To further engage users, the application includes a review system, allowing customers to leave feedback on books they have read. This feature helps other users make informed decisions based on ratings and reviews. Additionally, book categories, authors, and publishers are well-structured, making book discovery easier and more efficient.
By integrating essential e-commerce functionalities with interactive features such as wishlists and reviews, this project aims to create a modern, engaging, and accessible online bookstore. The system is designed to improve book accessibility, offer a smooth shopping experience, and provide users with a reliable platform for discovering, saving, reviewing, and purchasing books in an efficient and enjoyable way.